Graph-Based Neural Reconstruction from Skeletonized 3D Networks\\~\\\textit{Supplemental Material}

### 2018-03-12 papers/eccv2018/1_related_work.tex
papers: some updates based on HP comments

\paragraph{Pixel-based methods.}
A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}. 
These networks produce impressive accuracies but at a high computational cost.
Data augmentation in both training and testing can increase the prediction accuracy in boundary detection~\cite{zeng2017deepem3d}.
Lee et al. surpass the estimated human accuracy on the SNEMI3D dataset with a variant of the 3D U-Net architecture~\cite{lee2017superhuman}.

\paragraph{Region-based methods.}

@@

\paragraph{Error-correction methods.}
Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. 
We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

>>>>

\subsubsection{Pixel-based methods}
A significant amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. 
Some methods use a random forest populated with hand-designed features based on image characteristics around a given pixel to predict membrane probabilities~\cite{kaynig2015large}.
Most recent advancements use convolutional neural networks since machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
Originally, networks predicted membrane probabilities per each image slice using 2D convolutions~\cite{seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,kaynig2015large,amelio_segmentation}.
However, recent research extends these convolutions to include the z-dimension improving performance~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional}.
Many of these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron). 
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that goes from EM images directly to label volumes~\cite{januszewski2016flood}. 
These networks produce impressive accuracies but at a high computational cost.
Data augmentation in both training and testing can increase the prediction accuracy in boundary detection~\cite{zeng2017deepem3d}.
Lee et al. surpass the estimated human accuracy on the SNEMI3D dataset with a variant of the 3D U-Net architecture~\cite{lee2017superhuman}.

\subsubsection{Region-based methods}

@@

\subsubsection{Error-correction methods}
Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. 
We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

### 2018-03-12 papers/eccv2018/4_results.tex
papers: some updates based on HP comments

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
	\end{minipage}
	\caption{(left) Segments of neurons that were correctly merged by our method. (right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
	\label{fig:qualitative-results}
\end{figure}

@@

\paragraph{Inference Augmentation.}

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\begin{table}
	\begin{center}
		\begin{tabular}{c | c c c}
			Dataset & Precision & Recall & Accuracy \\ \hline
			Kasthuri & & & \\
			FlyEM Vol. 1 & & & \\
			FlyEM Vol. 2 & & & 
		\end{tabular}
		\caption{Data augmentation during test time increases the precision, recall, and accuracy of all three datasets.}
		\label{table:inference-augmentation}
	\end{center}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume. The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
	\label{fig:receiver-operating-characteristic}
\end{figure}

\paragraph{Generalization to Other Datasets.}

@@

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.32\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
	\end{minipage}
	\caption{(left) Segments of neurons before they were correctly merged by our method. (right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
	\label{fig:qualitative-results}
\end{figure}

@@

\subsubsection{Inference Augmentation}

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}		\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume. The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
	\label{fig:receiver-operating-characteristic}
\end{figure}

\subsubsection{Generalization to Other Datasets}

@@

\subsection{Computational Performance}

### 2018-03-12 papers/eccv2018/supplemental/classifier.tex
papers: some updates based on HP comments

>>>>

\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.0001 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{Training parameters.}
	\label{table:architecture}
\end{table}
